cleaning the pheno table

### 2020-11-10 scripts/37_clean_pheno_refreshed.Rmd
update

```{r}
#Oct/16/2019
#
#Loading patient info for Melody's project.
#
#

library('openxlsx');
library(data.table);

if(!exists("dt_carT_patient_info_with_sample_and_oligoID_time_stamp")){

@@

>>>>

This table has the CR_d100

```{r}
#Oct/16/2019
#
#Loading patient info for Melody's project.
#
#
library('openxlsx');
library(data.table);
if(!exists("dt_carT_patient_info_with_sample_and_oligoID_time_stamp")){

@@

CR:
day 30: msk and italy
day 100: upenn

Tox:
day 30: all of them

## getting the asv counts of those samples

```{r}
source('~/db_connect_simple.R')
connect_database(config_file = '~/dbConfig.txt')

get_table_from_database_predefined_filter('asv_counts_ag')
get_table_from_database('asv_sequences_ag')
```

```{r}
msk_cts <- asv_counts_ag %>% 
  filter(sampleid %in% msk$sampleid) %>% 
  select(asv_key, sampleid, count) %>% 
  spread(key = 'sampleid' , value = 'count', fill = 0)

# italy only has 3 in the db
italy_cts <- asv_counts_ag %>% 
  filter(sampleid %in% italy$oligoid) %>% 
  select(asv_key, sampleid, count) %>% 
  spread(key = 'sampleid' , value = 'count', fill = 0)

upenn_cts <- asv_counts_ag %>% 
  filter(sampleid %in% upenn$sampleid) %>% 
  select(asv_key, sampleid, count) %>% 
  spread(key = 'sampleid' , value = 'count', fill = 0)

# update italy pheno table
italy <- italy %>% 
  filter(oligoid %in% asv_counts_ag$sampleid)

```{r}
# write out the asv seq and cts to corresponding files
library(seqinr)
cts_fns <- list(msk = msk_cts,
                italy = italy_cts,
                upenn = upenn_cts)

cts_fns %>% 
  imap(function(.x, .y){

    # the cts for the asv
    .x %>% 
      write_tsv(str_glue('../data/picrust/input/{.y}_cts.tsv'))

    # the seqs for the asv
    seqs = asv_sequences_ag %>%
        filter(asv_key %in% .x$asv_key)

    write.fasta(sequences = as.list(seqs$asv_sequence),
              names = seqs$key,
              file.out = str_glue('../data/picrust/input/{.y}_seqs.tsv'))
  })
```
